%%
\smalltitle{Contributions to Open Source Scientific Projects}

\bulletbold{Brain Imaging Data Structure} organizing neuroimaging data and metadata to facilitate analysis and sharing.

\textbf{Role} Member of the team of maintainers of the specification, starter-kit, validator.

\textbullet Code: \githubicon{bids-standard}

\vspace{5mm}


\textbf{Role}: Maintainer

\bulletbold{bidspm} high-level functions to create MRI analysis pipeline of BIDS datasets using SPM.
\begin{itemize}
    \item repository: \githubicon{cpp-lln-lab/bidspm}
\end{itemize}
    
\bulletbold{bids-matlab} a Matlab and Octave toolbox to work with BIDS datasets.
\begin{itemize}
    \item repository: \githubicon{bids-standard/bids-matlab}
\end{itemize}

\bulletbold{bids2cite} Small python pacakage to create a citation files for a BIDS dataset.
\begin{itemize}
    \item repository: \githubicon{Remi-Gau/bids2cite}
\end{itemize}

\bulletbold{bidsMReye} BIDS app using deepMReye to decode eye motion for fMRI time series data. 
\begin{itemize}
    \item repository: \githubicon{cpp-lln-lab/bidsMReye}
\end{itemize}

\bulletbold{eCobidas} a webapp to facilitate transparent accurate methods reporting in neuroimaging.
\begin{itemize}
    \item repository: \githubicon{ohbm/cobidas}
    \item prototype: \webicon{https://ohbm.github.io/cobidas/}
    \item \doi{0.17605/osf.io/anvqy}
\end{itemize}

\bulletbold{bidsMReye} An Octave implementation of the mustache templating language for Octave that also happen to work with MATLAB.  
\begin{itemize}
    \item repository: \githubicon{Remi-Gau/Octache}
\end{itemize}

\bulletbold{clean matlab} A "clean code" template for MATLAB and Octave projects 
\begin{itemize}
    \item template repository: \githubicon{Remi-Gau/template_matlab_analysis}
    \item cookie cutter: \githubicon{Remi-Gau/cookiecutter_matlab_analysis}
\end{itemize}

\vspace{5mm}


%%
\smalltitle{Hackathon projects}

\bulletbold{eCobidas}
\begin{itemize}
    \item Brainhack Global Marseille 2021 (virtual) \webicon{https://brainhack.org/global2020/project/project_45/}
    \item Brainhack Global Donostia 2021 (virtual) \webicon{https://brainhack.org/global2020/project/project_45/}
    \item OpenMR Benelux 2020 (Rome, Nijmegen) \githubicon{OpenMRBenelux/openmrb2020-hackathon/issues/12}
    \item OHBM 2019 hackathon (Rome, Italy) \githubicon{ohbm/hackathon2019/issues/49}
\end{itemize}

\bulletbold{pre-registration template for MRI and M/EEG research}
\begin{itemize}
    \item SIPS 2019 (Rotterdam, Netherlands)
    % TODO
    % link to OSF
    % link to OHBM blog post
    % link to repo with final output
\end{itemize}
